Nail: A practical interface generator for data formats

### 2014-04-02 paper/intro.tex
minor nits in the intro

Third, data formats, especially binary formats such as PNG or PDF, can have \emph{structural dependencies}, such as offset, length and checksum fields
that are hard to express in state-of-the-art grammar languages. Often the programmer is required to
manually write control code, such as re-positioning the parser's input stream, looping over the
invocation of a sub-parser or computing a
checksum over raw input bytes.  Besides leaving much room for errors with offset arithmetic, such
code is usually not reusable when generating output.

@@

Second, this well-defined internal representation allows Nail to inverse the
parser and generate output. However, Nail allows \emph{constants} in the
external format to have multiple representations if they should not affect the
semantics of the data. For example, in a text protocol, the amount of
white-space separating tokens should not affect the meaning of the data and
consequently Nail does not expose it to the application. As long as
constants are only used for their intended purpose of representing syntax-only
features, the generated output will have the same semantics as the parsed input.

>>>>

Third, data formats, especially binary formats such as PNG or PDF, can have \emph{structural dependencies}, such as offset, length, and checksum fields
that are hard to express in state-of-the-art grammar languages. Often the programmer is required to
manually write control code, such as re-positioning the parser's input stream, looping over the
invocation of a sub-parser, or computing a
checksum over raw input bytes.  Besides leaving much room for errors with offset arithmetic, such
code is usually not reusable when generating output.

@@

Second, this well-defined internal representation allows Nail to invert the
parser and generate output. However, Nail allows \emph{constants} in the
external format to have multiple representations if they should not affect the
semantics of the data. For example, in a text protocol, the amount of
white-space separating tokens should not affect the meaning of the data and
consequently Nail does not expose it to the application. As long as
constants are only used for their intended purpose of representing syntax-only
features, the generated output will have the same semantics as the parsed input.
